Add Plant Functional Type (PFT) labels

### 2021-03-29 R/add_plant_functional_type.Rmd
still going

  else if(genusSpecies == "Acer circinatum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
              # or woody shrub? USDA Plants shows both Shrub and Tree growth form
    taxon_pft_lookup$commonName[i] = "vine maple"}

@@

  else if(genusSpecies == "Amelanchier laevis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "Allegheny serviceberry"}

  else if(genusSpecies == "Amyris elemifera"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "sea torchwood"}

@@

  else if(genusSpecies == "Bourreria sp."){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "strongbark"}

@@

  else if(genusSpecies == "Cercis canadensis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "eastern redbud"}

@@

  else if(genusSpecies == "Cornus drummondii"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "roughleaf dogwood"}

  else if(genusSpecies == "Cornus florida"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "flowering dogwood"}

@@

  else if(genusSpecies == "Frangula purshiana"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "Cascara buckthorn"}

@@

  else if(genusSpecies == "Ilex montana"){
    taxon_pft_lookup$pft[i] = "NA"
    taxon_pft_lookup$commonName[i] = "mountain holly"}

@@

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

@@

  else if(genusSpecies == "Prunus serotina"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "black cherrt"}

>>>>

  else if(genusSpecies == "Acer circinatum"){
    taxon_pft_lookup$pft[i] = "NA " ??? 
    taxon_pft_lookup$commonName[i] = "vine maple"}

@@

  else if(genusSpecies == "Amelanchier laevis"){
    taxon_pft_lookup$pft[i] = "???" ???
    taxon_pft_lookup$commonName[i] = "Allegheny serviceberry"}

  else if(genusSpecies == "Amyris elemifera"){
    taxon_pft_lookup$pft[i] = "???"     ???
    taxon_pft_lookup$commonName[i] = "sea torchwood"}

@@

  else if(genusSpecies == "Bourreria sp."){
    taxon_pft_lookup$pft[i] = "???"   ???
    taxon_pft_lookup$commonName[i] = "strongbark"}

@@

  else if(genusSpecies == "Cercis canadensis"){
    taxon_pft_lookup$pft[i] = "???"   ???
    taxon_pft_lookup$commonName[i] = "eastern redbud"}

@@

  else if(genusSpecies == "Cornus drummondii"){
    taxon_pft_lookup$pft[i] = "???"    ???
    taxon_pft_lookup$commonName[i] = "roughleaf dogwood"}

  else if(genusSpecies == "Cornus florida"){
    taxon_pft_lookup$pft[i] = "???"    ???
    taxon_pft_lookup$commonName[i] = "flowering dogwood"}

@@

  else if(genusSpecies == "Frangula purshiana"){
    taxon_pft_lookup$pft[i] = "???"     ???
    taxon_pft_lookup$commonName[i] = "Cascara buckthorn"}

@@

  else if(genusSpecies == "Ilex montana"){
    taxon_pft_lookup$pft[i] = "???"          ???
    taxon_pft_lookup$commonName[i] = "mountain holly"}

  else if(genusSpecies == "Ilex opaca"){
    taxon_pft_lookup$pft[i] = "woody_shrub"   ???      # broadleaved evergreen tree
    taxon_pft_lookup$commonName[i] = "American holly"}

  else if(genusSpecies == "Juniperus osteosperma"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "Utah juniper"}

  else if(genusSpecies == "Larix sp."){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "larch"}

  else if(genusSpecies == "Larrea tridentata"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "creosote bush"}

  else if(genusSpecies == "Liquidambar styraciflua"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sweetgum"}

  else if(genusSpecies == "Liriodendron tulipifera"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "tuliptree"}

  else if(genusSpecies == "Maclura pomifera"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"   # small deciduous tree or large shrub
    taxon_pft_lookup$commonName[i] = "Osage-orange"}

  else if(genusSpecies == "Mangifera indica"){
    taxon_pft_lookup$pft[i] = "???"       ???   # broadleaf evergreen tree
    taxon_pft_lookup$commonName[i] = "mango"}

  else if(genusSpecies == "Melia azedarach"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "Chinaberrytree"}

  else if(genusSpecies == "Morus rubra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "red mulberry"}

  else if(genusSpecies == "Nyssa aquatica"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "water tupelo"}

  else if(genusSpecies == "Nyssa biflora"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "swamp tupelo"}

  else if(genusSpecies == "Nyssa sylvatica"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "blackgum"}

@@

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft[i] = "???"              ???
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

@@

  else if(genusSpecies == "Prunus serotina"){
    taxon_pft_lookup$pft[i] = "???"       ???
    taxon_pft_lookup$commonName[i] = "black cherry"}
